%%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume 
\documentclass[margin,line]{resume}
\pagestyle{myheadings}
\usepackage{comment}
\usepackage{hyperref}
\usepackage{comment}
\hypersetup{
  colorlinks, linkcolor=blue
}

%______________________________________________________________________________________________________________________
\begin{document}

\name{\Large Eleftheria (Ria) Kontou, Ph.D.}
\begin{resume}
    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle \bf CONTACT\\INFO}
		   Address: 205 N. Mathews Ave, MC 250, Room 1212 Newmark CE Lab, Urbana, IL 61801, USA  \vspace{0mm}\\\vspace{0mm}%
                       E-mail: \href{mailto:kontou@illinois.edu}{kontou@illinois.edu}  | Office phone: +1 217-244-3425     \vspace{0mm}\\\vspace{0mm}%
    Webpage: \url{https://publish.illinois.edu/kontou/home}  \vspace{0mm}\\\vspace{-1mm}%
    

%
    % Education
 	  \vspace{-0.2in}
    \section{\mysidestyle \bf ACADEMIC POSITIONS}
     \textbf{Assistant Professor}  \hfill \textbf{Oct 2019--Present}\vspace{-3mm}\\\vspace{-1mm}%
    \\  Department of Civil and Environmental Engineering
    \\ \textbf{University of Illinois at Urbana-Champaign} Urbana, IL, USA \\
    
     %\textbf{Postdoctoral Researcher}  \hfill \textbf{Aug 2018--Oct 2019}\vspace{-3mm}\\\vspace{-1mm}%
    %\\  Department of City and Regional Planning
    %\\ \textbf{University of North Carolina at Chapel Hill} Chapel Hill, NC, USA \\
   % \vspace{-0.2in}
    
      %   \textbf{Postdoctoral Research Associate}  \hfill \textbf{Jan 2017--Aug 2018}\vspace{-3mm}\\\vspace{-1mm}%
    %\\  Transportation and Hydrogen Systems Center
    %\\ \textbf{National Renewable Energy Laboratory} Golden, CO, USA \\
   % \vspace{-0.2in}
    
     	  \vspace{-0.2in}

    \section{\mysidestyle \bf EDUCATION}

    \textbf{Department of Civil and Coastal Engineering}, \textbf{University of Florida} \hfill \textbf{Dec 2016}\vspace{-3mm}\\\vspace{-1mm}%
   \\ \textbf{Ph.D. in Civil Engineering} (Transportation Systems) \\
        Dissertation: \emph{Socially Optimal Policies for Light-Duty Vehicle Electrification and Operations} \\
        Advisor: \emph{Prof. Yafeng Yin}
        
         %   
        
     \textbf{Department of Civil and Environmental Engineering}, \textbf{Virginia Tech} \hfill \textbf{Dec 2013}\vspace{-3mm}\\\vspace{-1mm}%
 \\ \textbf{M.Sc. in Civil Engineering} (Transportation Systems)\\
Thesis: \emph{Commute Travel Changes and their Duration in Hurricane Sandy's Aftermath} \\
   Advisor: \emph{Prof. Pamela Murray-Tuite}
	%    \vspace{-0.2in}

     \textbf{Department of Civil Engineering}, \textbf{National Technical University of Athens} \hfill \textbf{Dec 2011}\vspace{-3mm}\\\vspace{-1mm}%
\\  \textbf{Diploma in Civil Engineering} \\
Thesis: \emph{Allocation of Buses to Depots: a Mixed Integer Non-Linear Programming Approach} \\
   Advisor: \emph{Prof. Matthew Karlaftis}
	

%__________________________________________________________________________________________________________________
    % Research Interests

    \section{\mysidestyle \bf RESEARCH\\EXPERIENCE}

    \vspace{-0.1in}
    
     \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.6in}\= \kill% set up two tab positions
    {\bf Postdoctoral Researcher} \>   City and Regional Planning   \> \bf Aug 2018--Oct 2019 \\
                      \>{\bf University of North Carolina at Chapel Hill} \\ \> Chapel Hill, NC, USA
   \end{tabbing}\vspace{-20pt}

%     \begin{itemize}
 %  \item Electrification equity: composite scores and implications for policy, finalist for receiving funding from Lee Schipper Memorial Scholarship by World Resources Institute
 %\item Active school transportation patterns analytics and logit choice modeling in the US and internationally, funded by Federal Highway Administration (FHWA)
 % \item  Transportation safety and ridesourcing use relationships using econometrics, funded through Collaborative Sciences Center for Road Safety
  %  \end{itemize}


     \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Postdoctoral Researcher} \>  Transportation Systems Center \> \bf Jan 2017--Aug 2018\\
                          \>{\bf National Renewable Energy Laboratory} \\ \> Golden, CO, USA
   \end{tabbing}\vspace{-20pt}

%   \begin{itemize}
%\item Modeled demand for future, electrified, ride-hailing services for the smart city of Columbus OH \& Austin TX and geospatial analysis of trip generations via spatial error regression models, funded by the Department of Energy (DOE)
 % \item Published connected \& automated vehicles \& technologies (e.g., cooperative adaptive cruise control; eco-signal implementation; auto-taxi usage) energy consumption analysis results using micro-simulation and macroscopic data, funded by DOE
  % \item Modeled the California Zero Emission Vehicle mandate policy and uncovered potential significance on vehicle ownership of alternative fuel vehicles via a multinomial logit fit; handled all communications with the sponsoring agency, the California Energy Commission (CEC)
 %\item Performed financial analysis for electric vehicle high-power fast chargers, with and without collocation of energy storage and photovoltaics for a case study in San Diego CA, for CEC
% \item Reported spatial heterogeneity of electricity costs applicable to electric vehicle fast charging using NREL's Utility Rate Database, funded by DOE
   % \end{itemize}

    
     \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Graduate Assistant} \> Center for Transportation Analysis \> \bf  Aug 2015--Aug 2016\\
                    \>  \bf Oak Ridge National Laboratory   \\   \> Knoxville, TN, USA
   \end{tabbing}\vspace{-20pt}

 %   \begin{itemize}
  %  \item Modeled and validated market acceptance of advanced automotive technologies with a nested logit model
  %  \item Developed an optimization model for max public chargers' visibility, using urban on-street parking lot data for a subset of U.S. cities
  %  \end{itemize}

    \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Research Assistant} \> Civil Engineering \> \bf Jan 2014--Dec 2016\\
                          \> {\bf University of Florida} \\ \> Gainesville, FL, USA
   \end{tabbing}\vspace{-20pt}

 %   \begin{itemize}
  %   \item	Developed socially optimal policies supporting electric vehicles adoption and operation (including optimal electric range, charging placement and incentives schemes determination) and ran U.S. market application simulations, funded by Lloyd's Register Foundation (LRF)
  %  \item	Developed cost-effective and eco-friendly electric vehicle charging management models; applied methods to U.S. regions considering driving and activity patterns heterogeneity, funded by LRF
%\item	Completed cost-benefit analysis for adaptive traffic signal control (ATSC) implementation of a statewide Florida Department of Transportation (FDOT) project
%\item	Led team for survey development and interview conduct that identified of agencies needs for the deployment of ATSC, for a FDOT project
%\item	Simulated an 11-intersection corridor with ATSC in Gainesville, FL and evaluated travel time and throughput changes, funded by FDOT
 %   \end{itemize}

     \begin{tabbing}
     \hspace{2.0in}\= \hspace{2.6in}\=\kill
     {\bf Research Assistant}\> Turner-Fairbank Highway \> \bf Aug 2012--Aug 2013\\
     \>Research Center\\
     \> \bf Federal Highway Administration \>  \\
\> McLean, VA, USA
    \end{tabbing}\vspace{-20pt}

%        \begin{itemize}
%\item	 Uncovered drivers' distractions and addressed safety concerns in arterials through naturalistic eye-tracking data, funded by FHWA
 % \item Simulated of alternative intersection designs (e.g., mini-roundabouts) using VISSIM, funded by FHWA
  %  \end{itemize}

        \begin{tabbing}
   \hspace{2.0in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Research Assistant} \> Civil Engineering \> \bf Jul 2012--Dec 2013\\
                          \> {\bf Virginia Tech}\\ \> Falls Church, VA
   \end{tabbing}\vspace{-20pt}
 %       \begin{itemize}
  %  \item Modeled commute travel behavior in the aftermath of Hurricane Sandy for the New York City Statistical Metropolitan Area using econometrics; funded by National Science Foundation (NSF)\\
  %  \end{itemize}


    %__________________________________________________________________________________________________________________
        %__________________________________________________________________________________________________________________
        % Publications

   	    \vspace{-1pt}
   \section{\mysidestyle  \bf  PUBLICATIONS}
   \vspace{-2pt}
   
   \subsection{\mysidestyle \bf Referred Articles}
\begin{itemize}
\item {\bf Kontou, E.}, Garikapati, V., and Hou, Y. Reducing ridesourcing empty vehicle travel with future travel demand prediction. Transportation Research Part C: Emerging Technologies, Vol. 121, 102826, 2020. \href{https://doi.org/10.1016/j.trc.2020.102826}{Link}
\item Greene, D. L., {\bf Kontou, E.}, Borlaug, B., Brooker, A., and Muratori. M. Public charging infrastructure for plug-in electric vehicles: What is it worth? Transportation Research Part D: Transport and Environment, Vol. 78, pp. 102182, 2020. \href{https://doi.org/10.1016/j.trd. 2019.11.011}{Link}
\item Muratori, M., {\bf Kontou, E.}, and Eichman, J. Electricity Rates for Electric Vehicle Direct Cur- rent Fast Charging in the United States. Renewable and Sustainable Energy Reviews, Vol. 113, pp. 109–235, 2019. \href{https://doi.org/10.1016/j.rser.2019.06.042}{Link}
\item Wenzel, T., Rames, C., {\bf Kontou, E.}, and Henao, A. Travel and Energy Implications of a Ride-sourcing Service in Austin, Texas. Transportation Research Part D: Transport and Environment., Vol. 70, pp. 18–34, 2019. \href{https://doi.org/10.1016/j.trd.2019.03.005}{Link}
\item {\bf Kontou, E.}, Liu, C., Xie, F., Wu, X., and Lin, Z. Understanding the Linkage between Electric Vehicle Charging Network Coverage and Charging Opportunity Using GPS Travel Data. Transportation Research Part C: Emerging Technologies, Vol. 98, pp. 1–13, 2019. \href{https://doi.org/10.1016/j.trc.2018.11.008}{Link}
\item Wood, E., Rames, C., {\bf Kontou, E.}, Motoaki, Y., Smart, J., Zhou, Z. Analysis of Fast Charging Station Network for Electrified Ride-Hailing Services. SAE Technical Paper 0067, 2018. \href{https://doi.org/10.4271/2018-01-0667}{Link}
\item {\bf Kontou, E.}, Yin, Y., Lin, Z., and He, F. Socially optimal replacement of conventional with electric vehicles for the US household fleet. International Journal of Sustainable Transportation, Vol. 11, No. 10, pp. 749–763, 2017. \href{https://doi.org/10.1080/15568318.2017.1313341}{Link}
\item {\bf Kontou, E.}, Yin, Y., and Ge, Y. Cost-Effective and Eco-Friendly Plug-in Hybrid Electric Charging Management. Transportation Research Record: A Journal of the Transportation Re- search Board, Vol. 2628, pp. 87–98, 2017. \href{https://doi.org/10.3141/2628-10}{Link}
\item {\bf Kontou, E.}, Murray-Tuite, P., and Wernstedt, K. Duration of commute travel changes in the aftermath of Hurricane Sandy using accelerated failure time modeling. Transportation Research Part A: Policy and Practice, Vol. 100, pp. 170–181, 2017. \href{https://doi.org/10.1016/j.tra. 2017.04.015}{Link}
\item {\bf Kontou, E.}, Murray-Tuite, P., and Wernstedt, K.Commuter Adaptation in Response to Hurricane Sandy’s Damage. Natural Hazards Review, Vol. 18, No. 2, pp. 04016010, 2016. \href{https://doi.org/10.1061/(ASCE)NH.1527-6996.0000231}{Link}
\item {\bf Kontou, E.}, Yin, Y., and Lin, Z. Socially Optimal Electric Driving Range of Plug-In Hybrid Electric Vehicles. Transportation Research Part D: Transport and Environment, Vol. 39, pp. 114–125, 2015. \href{https://doi.org/10.1016/j.trd.2015.07.002}{Link}
\item {\bf Kontou, E.}, Kepaptsoglou, K., Charalampakis, A., and Karlaftis, M. The bus to depot allocation problem revisited: a genetic algorithm. Public Transport, Vol. 6, No. 3, pp. 237–255, 2014. \href{https://doi.org/10.1007/s12469-013-0078-4}{Link}
\item {\bf Kontou, E.}, and Zhang, W. Isolating Stationary and Temporal Sources of Driver Distraction through Eye-Tracking Study. Advances in Transportation Studies, Vol. 1, pp. 87–100, 2014.
\end{itemize}
	    \vspace{-0.3in}
   \subsection{\mysidestyle \bf Book Chapters}
\begin{itemize}
\item McDonald, N., {\bf Kontou, E}, and Handy, S. (2021). Children and Cycling. In Pucher J. & Buehler R. (Eds.), Cycling for Sustainable Cities. Cambridge, Massachusetts; London, England: The MIT Press. ISBN 9780262542029.
\item Stephens T.S., Auld, J., Chen, Y., Gonder, J., {\bf Kontou, E.}, et al. Assessing Energy Impacts of Connected and Automated Vehicles at the U.S. National Level:Preliminary Bounds and Proposed Methods. In: Meyer G., Beiker S. (eds) Road Vehicle Automation 5. Lecture Notes in Mobility. Springer, Cham, 2019. \href{https://link.springer.com/chapter/10.1007/978-3-319-94896-6_10}{Link}
\end{itemize}
    \vspace{-0.3in}
\subsection{\mysidestyle \bf Indicative Presentations}
\begin{itemize}
\item Alternative Fuel Vehicles Evacuation Planning (with \underline{Purba D.}) At the {\em INFORMS Annual Meeting}, Virtual, Nov 8-13, 2020.
\item Electricity rates for electric vehicle fast charging (with Muratori M. and Eichman. J.). At the {\em 6th Annual Conference on Transportation, Economics, Energy and the Environment} (TE3), University of Michigan, MI, Oct 18, 2019.
 \item Analysis of Fast Charging Station Network for Electrified Ride-Hailing Services (with Wood, E., Rames, C., Motoaki, Y., Smart, J. and Zhou, Z.). At the {\em Society of Automotive Engineers World Congress}, Detroit MI, April 10-12, 2018.
\item Incentive Schemes for Maximizing the Benefits from Battery Electric Vehicle Adoption (with Yin, Y.). At the {\em INFORMS Annual Meeting}, Houston TX, October 22-25, 2017.
\item Quantifying Fuel Impacts of Connected and Automated Vehicles Through a Bottom-up Energy Inventory Model and National Traffic Data (with Gonder, J. and Chen, Y.). At the {\em Autonomous Vehicle Symposium 2017}, San Francisco CA, July 11-17 2017.
\item Shared Autonomous Mobility: A Review of Potential Economic Impacts and Energy Savings (with Gonder, J.). At the {\em 14th Annual Colorado Transportation Symposium}, Denver CO, April 7 2017.
\item Public Charging Opportunities Frontiers for U.S. Cities (with Lin, Z., Liu, C. and Yin, Y.), At the {\em 96th Annual Meeting of the Transportation Research Board}, Washington DC, January 8-12 2017.
\item Socially Optimal Replacement of Conventional Vehicles with Electric Vehicles for the U.S. Household Fleet (with Yin, Y.) At the {\em Lloyd's Register Foundation International Workshop on Transport and Environment}, Shanghai Maritime University, Shanghai China, August 2-3 2015.
\end{itemize}


%\subsection{\mysidestyle Articles In Preparation/Submitted}
%\begin{itemize}
%
%
%\item
%\end{itemize}
%\vspace{-20pt}

   %\vspace{-20pt}
    \vspace{-0.3in}
\subsection{\mysidestyle \bf Referred Reports}

\begin{itemize}
\item {\bf Kontou, E.}, Melaina, M., and Brooker A. Light Duty Vehicle Attribute Projections (Years 2015-2030). California Energy Commission. CEC-200-2018-008 Report, 2018. \href{https://www.nrel.gov/docs/fy18osti/70455.pdf}{Link}
\item Stephens, T. S., Levinson, R. S., Brooker, A., Liu, C., Lin, Z., Birky, A., and {\bf Kontou, E.} Comparison of Vehicle Choice Models. ANL/ESD-17/19 Report, 2017. \href{https://www.osti.gov/biblio/1418338}{Link}

\end{itemize}
    \vspace{-0.3in}
\subsection{\mysidestyle \bf Under Review}

\begin{itemize}

\item {\bf Kontou, E.} and McDonald, N. Associating Ridesourcing with Road Safety Outcomes: Insights from Austin Texas. Target journal: {\em PLOS One}

\item \underline{Guo, S.} and {\bf Kontou, E.} Disparities and Equity Issues in Electric Vehicles Incentives Allocation. Target journal: {\em Energy Policy}

\end{itemize}
\\
    \vspace{-0.2in}
Students names are underlined.
    

%__________________________________________________________________________________________________________________


    %__________________________________________________________________________________________________________________
    % Professional Experience
 \vspace{-0.2in}
\section{\mysidestyle \bf INVITED LECTURES}
  \begin{itemize}
  \item Socioresilient Infrastructure Session, Systems Session Facilitator, \textbf{MIT \& Station 1 NSF Convergence Accelerator Workshop}, Virtual, Sep 25 2020
  \item Examining Needs for Infrastructure Development: Commissioner Workshop on Plug-in Electric Vehicle Charging Infrastructure, \textbf{California Energy Commission}, Virtual, Aug 6 2020 \href{https://www.energy.ca.gov/event/workshop/2020-08/session-4-examining-needs-infrastructure-development-commissioner-workshop}{Link}
  \item Next Generation Transportation Systems Seminar, \textbf{University of Michigan}, Virtual, Mar 26 2020 \href{https://events.umich.edu/event/70249}{Link}
  \item \textbf{Sloan Foundation and Boston University Workshop} on Integrating New Electric Mobility Systems with the Electric Grid Infrastructure, MA, Nov 6-7 2019 \href{http://www.bu.edu/systems/sloan-foundation-november-6-2019-agenda-day-1/}{Link}
  \item Data for Good Exchange 2019, \textbf{Bloomberg's Global Headquarters}, NY, Sep 15 2019 \href{https://www.techatbloomberg.com/blog/data-for-good-exchange-2019-preview-people-track/}{Link}
    \item 3 Revolutions Future Mobility Research Workshop, \textbf{UC Davis}, CA, Oct 23-24 2018\\
Impacts of travel demand information diffusion on reducing empty vehicle miles traveled by ride-sourcing vehicles
\item UNC CleanTech Summit, \textbf{UNC Chapel Hill}, NC, Mar 1-2 2018\\
Smart \& Healthy Cities Panel on the Electrification of the Economy
\end{itemize}


\section{\mysidestyle \bf GRANTS}
    \vspace{-0.2in}
    \subsection{\mysidestyle \bf Research}
       \vspace{-0.2in}
     \textbf{Integrated Modeling and Technoeconomic Assessment of Electric Vehicle \\ Community Charging Hubs}  \hfill \textbf{2020--23}\vspace{-0mm}\\\vspace{-0mm}%
 {\bf Department of Energy Vehicle Technologies Office}, \$280,000 (Total \$350,000) \\
 PI with Co-PI Yan (Joann) Zhou (Argonne National Laboratory)
 
 \textbf{Escaping Transport and Fuel Poverty: A Novel Framework for Transportation Energy Vulnerability Analysis}  \hfill \textbf{2020--21}\vspace{-0mm}\\\vspace{-0mm}%
 {\bf Center for Social and Behavioral Science UIUC}, \$19,882 \\
 PI with Julie Cidell (co-PI) and Michael Minn (co-PI) (all UIUC)

 \textbf{Planning for Emerging Mobility: Testing and Deployment in Illinois.}  \hfill \textbf{2020--21}\vspace{-0mm}\\\vspace{-0mm}%
 {\bf Illinois Department of Transportation}, \$25,000 (Total \$650,000) \\
 Co-PI with PI Imad Al-Qadi (UIUC), Co-PIs Ghassan Chehab, Angeli Jayme, Lewis Lehe, and Yanfeng Ouyang (all UIUC)

 \textbf{Spatial Modeling of Covid-19: Optimizing PDE and Metapopulation Models\\ for Prediction and Spread Mitigation}  \hfill \textbf{2020--21}\vspace{-0mm}\\\vspace{-0mm}%
 {\bf C3.ai Digital Transformation Institute}, \$50,000 (Total \$200,000) \\
 Co-PI with PI Zoi Rapti (UIUC), Co-PIs Panos Kevrekidis (UMass Amherst), Yannis Kevrekidis (Johns Hopkins)
    \vspace{-0.2in}
    \subsection{\mysidestyle \bf Teaching}
       \vspace{-0.2in}
     \textbf{PrairieLearn and Course Redesign for Core CEE Intro Sequence}  \hfill \textbf{2020--21}\vspace{-0mm}\\\vspace{-0mm}%
 {\bf Strategic Instructional Innovations Program GCOE UIUC}, Total \$34,000 \\
 Co-PI with PI Sotiria Koloutsou-Vakakis, Co-PIs Hadi Meidani, Lei Zhao, Christopher Tessum (all CEE UIUC)
  %__________________________________________________________________________________________________________________
    % Computer Skills
   % \section{\mysidestyle \bf OTHER\\SKILLS} 

      %Matlab, Python, R, QGIS, \LaTeX, SQL, Tableau, Office, VISSIM, TransCAD, git


\section{\mysidestyle \bf TEACHING}
  \vspace{0pt}
\begin{itemize}
	\item {\bf Instructor CEE 598: Urban Transportation Models Graduate course}, \\
	University of Illinois at Urbana-Champaign, Fall 2020
	\item {\bf Instructor CEE 201: Systems Engineering and Economics BSc course}, \\
	University of Illinois at Urbana-Champaign, Spring 2020
	\item {\bf Co-Instructor (with Leta Huntsinger) PLAN 739: Transportation Planning Models}, \\
	MSc course, University of North Carolina at Chapel Hill, Spring 2019
	\item  \textbf{Teaching Assistant TTE 5305: Transportation Systems Analysis}, \\
	MSc course taught by Yafeng Yin, University of Florida, Fall 2014 & Fall 2015
	\end{itemize}
	
	     \section{\mysidestyle \bf AWARDS} 
%
  \vspace{0pt}
    \begin{itemize}
\item \textbf{iSEE Levenick Teaching Fellowship}, Sustainability Teaching Fellow, UIUC, 2020 \href{https://sustainability.illinois.edu/about/partnerships/levenick-isee-fellows-program/}{Link}
\item \textbf{Cloud Research Support Engineer Honorarium}, Pervasive Technology Institute, Indiana University, 2019 \href{https://educationblog.microsoft.com/en-us/2019/02/announcing-a-1m-grant-to-advance-the-role-of-humanware-in-academic-research/}{Link}
\item \textbf{Scholar}, Collaborative Sciences Center for Road Safety, UNC Chapel-Hill, 2018-19
\item \textbf{Reviewer Recognition}, TRB Committee on Alternative Transportation Fuels and Technologies, 2017 and 2018
\item \textbf{Executive Fellow}, International Road Federation (IRF), 2017
\item \textbf{Future Industry Leader Spotlight Award}, American Road & Transportation Builders Association, 2016
\item  \textbf{Precourt Fellowship}, Stanford’s Energy Efficiency Center for the 2016 Behavior, Energy and Climate Change Conference (BECC) Travel Grant, 2016
\item \textbf{Clinton Global Initiative University (CGIU) Travel Grant} for CGIU Conference, 2016
\item \textbf{Fellow}, University of Florida Transportation Institute (UFTI), 2014-16
\item \textbf{Gerondelis Foundation Scholar} Gerondelis Foundation, 2014
\item \textbf{Finalist of the Graduate Collegiate Poster Competition}, Society of Women Engineers, 2014
\item \textbf{Greek State Scholarships Fellow}, State Scholarship Foundation, 2012-13
\end{itemize}    

  %__________________________________________________________________________________________________________________	

\section{\mysidestyle \bf SERVICE}
  \vspace{-12pt}
\subsection{\mysidestyle \bf National-level}
\begin{itemize}
	\item The {\bf National Academies of Sciences, Engineering, Medicine, Transportation Research Board}, Standing Committee on Alternative Transportation Fuels and Technologies (AMS40), Member, 2017-23
	
\item The {\bf National Academies of Sciences, Engineering, Medicine, Transportation Research Board}, Young Member Coordinating Council, Chair, 2021-23

\item {\bf American Society of Civil Engineers (ASCE)} Transportation & Development Institute, Connected and Autonomous Vehicles Impacts Committee, Younger Member, 2015-20
%\item {\bf Transportation Research Board}, Young Members Council: Planning and Environment Group, Member 2015-19
	\end{itemize}
	  \vspace{-25pt}
	\subsection{\mysidestyle \bf Campus}
\begin{itemize}
\item Illinois Climate Action Plan (iCAP) Transportation SWATeam Member, 2020-21
	\end{itemize}
		  \vspace{-25pt}
\subsection{\mysidestyle \bf College}
\begin{itemize}
\item Grainger College of Engineering Diversity Committee, Member, 2020-21
\item Anti-Racism Task Force (lead: Tandy Warnow CS), Member, Jun-Aug 2020
	\end{itemize}
		  \vspace{-25pt}
\subsection{\mysidestyle \bf Department}
\begin{itemize}
\item EWES Program Graduate Admissions Coordinator, 2020-21
\begin{itemize}
	\end{itemize}

	\section{\mysidestyle \bf ASSOCIATIONS}
  \vspace{-5pt}
  \begin{itemize}
 		\item { \bf American Society of Civil Engineers (ASCE)}, Associate Member, 2016-Present
		\item {\bf Women's Transportation Seminar (WTS)}, Member, 2014-Present

\end{itemize}		
\section{\mysidestyle \bf REVIEWS}	
Serving as a reviewer for:  
 \vspace{0pt}

	\begin{numerate}
	\item \textbf{Research Proposals}
			\begin{itemize}
		\item Sloan Foundation Proposal Review 2020
		\item National Science Foundation Engineering Review Panel 2020
		\item  DOE Vehicle Technologies Office, Annual Merit Review, Transportation Analysis Reviewer, 2019 and 2020
		\item National Cooperative Highway Research Program, Project Panel: Initiating the Systems Engineering Process for Rural Connected Vehicle Corridors, Final Project Reviewer, 2020
		\item Southeastern Transportation Research, Innovation, Development and Education Center Proposal Review 2020
		\item UCLA Institute of Transportation Studies Proposal Review 2019
		\item Mountain-Plains Consortium University Transportation Center Publication Peer Review 2019
	\end{itemize}

	\item \textbf{Journal Articles}
	\begin{itemize}
		\item Energy Reports
		\item Environmental Research Letters
		\item IEEE Transactions on Intelligent Transportation Systems
		\item IEEE Intelligent Transportation Systems Magazine
		\item IET Intelligent Transport Systems
		\item International Journal of Sustainable Transportation
		\item International Journal of Transportation Science and Technology
		\item International Journal of Urban Sustainable Development
		\item Journal of Cleaner Production
		\item Sustainability
		\item Sustainable Cities and Societies
		\item Transport Policy
		\item Transportation
		\item Transportation Research Part A: Policy and Practice
		\item Transportation Research Part C: Emerging Technologies
		\item Transportation Research Part D: Transport and Environment
		\item Transportation Research Record: A Journal of the Transportation Research Board
			\end{itemize}
				\end{numerate}

%\end{itemize}


%__________________________________________________________________________________________________________________
    % Referees
%    \\

 
%\newpage   
%

%\section{\mysidestyle \bf REFERENCES} 
%
%\begin{itemize}
%	\item \textbf{Dr. Yafeng Yin} \\
%Professor\\
%Department of Civil and Environmental Engineering \\
%University of Michigan \\
%Email: yafeng@umich.edu \\
%Phone number: (734) 764 - 8249
%
%	\item \textbf{Dr. Noreen McDonald} \\
%Thomas Willis Lambeth Distinguished Professor \\ \& Director of Carolina Transportation Program\\
%Department of City and Regional Planning\\
%University of North Carolina at Chapel Hill \\
%Email: noreen@unc.edu \\
%Phone number: (919) 962 - 4781
%	
%	\item \textbf{Dr. Lily Elefteriadou} \\
%	Barbara Goldsby Professor  \& UF Transportation Institute Director\\
%Department of Civil and Coastal Engineering \\
%University of Florida \\
%Email: elefter@ce.ufl.edu \\
%Phone number:  (352) 294 - 7802
%
%
%\item \textbf{Dr. Zhenhong Lin} \\
%Senior Researcher at the Center for Transportation Analysis\\
%Adjunct Associate Professor of Industrial and Systems Engineering at University of Tennessee, Knoxville \\
%National Transportation Research Center, Oak Ridge National Laboratory \\
%Emai: linz@ornl.gov \\
%Phone number: (865) 946 - 1308
%
%
%\item \textbf{Dr. Pamela Murray-Tuite} \\
%Associate Professor\\
%Department of Civil Engineering \\
%Clemson University \\
%Email: pmmurra@clemson.edu \\
%Phone number:  (864) 656 - 3802
%


\end{itemize}




%______________________________________________________________________________________________________________________


%\section{\mysidestyle Professional References} 




%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
